Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed another typo.
[ paper ] metis-intro improved.

\Metis is an automatic theorem prover for first-order logic with equality
developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}.
This prover is suitable for proof reconstruction since it provides well-documented proofs to justify its deduction steps from the basis of only six inference rules. In Fig.~\ref{fig:metis-inferences}, we show the three \Metis rules for propositional logic.

@@

We present the list of inference rules used by \Metis in
the \TSTP derivations for propositional logic
in Table~\ref{tab:agda-metis-table}.
We reconstruct these rules in Section~\ref{sec:proof-reconstruction}.
The reader may notice that the
inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
rules in aforementioned table. However, the former rules are
implemented by the latter rules. For instance, as far as we know, in
\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
rules that represent the \emph{axiom} rule by \Metis.

>>>>

\Metis is an automatic theorem prover for first-order logic with equality
developed by  \citeauthor{hurd2003first}~\cite{hurd2003first}. This prover is
suitable for proof-reconstruction since it provides well-documented proofs to
justify its deduction steps from the basis of only six inference rules for
first-order logic (see, for example, \cite{paulson2007source,Farber2015}). For
the propositional fragment, \Metis has three inference rules,
see Fig.~\ref{fig:metis-inferences}.

@@

We present the list of inference rules used by \Metis in
the \TSTP derivations for propositional logic
in Table~\ref{tab:agda-metis-table}.
We reconstruct these rules in Section~\ref{sec:proof-reconstruction}.
The reader may notice that the
inference rules presented in Fig~\ref{fig:metis-inferences} diverge from the
rules in aforementioned table. However, the former rules are
implemented by the latter rules. For instance, as far as we know, in
\TSTP derivations, \canonicalize, \clausify, \conjunct, and \simplify, are all
the rules that represent the \emph{axiom} rule by \Metis.
